DESING AND SIMULATION SOFTWARE FOR RHODOTRON TYPE ELECTRON ACCELERATORS

### 2023-08-07 subsections/simulation/poc/poc.tex
başlık eklendi

This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
\begin{itemize}
    \item Get electron energy $E_{in}$
    \item Get the RF field definitions
    \item Get the magnet design parameters if there is any
    \item Do following until the simulation time has ellapsed
    \begin{enumerate}
        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
        \item Calculate new $E_t$
    \end{enumerate}
\end{itemize}

The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
\begin{figure}[H]
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
        for (double t=0; t<SimuTime; t+=dT){
            double RelBeta  = v/c;
            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);

@@

            RelBeta  = v/c;
            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
            Et=RelGamma*E0; 
        }
    \end{minted}
    \caption{Core logic loop of the POC}
    \label{fig:POC_core_logic}
\end{figure}

After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
% 40 kW total power
% Emax = 0.96 in old, 2.08 in new version
% R1 = 0.1882
% R2 = 0.753
% f = 107.5
\begin{figure}[H]
    \begin{eqnarray}
        E_{Pottier} &=& 0.565 MeV \nonumber\\
        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
        E_{POC} &=& 0.873 MeV \nonumber
    \end{eqnarray}
    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
\end{figure}

As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
Since using a single software would have made the process error prone.

>>>>

This proof of concept worked with interacting an electron with the EM field provided, at discrete time steps $dt$. The core sequence of this software is provided below.
Where $\vecthreeBF{r}$ is the position, $\vecthreeBF{v}$ is the velocity of the $e^-$;
\begin{itemize}
    \item Get electron energy $E_{in}$
    \item Get the RF field definitions
    \item Get the magnet design parameters if there is any
    \item Do following until the simulation time has ellapsed
    \begin{enumerate}
        \item Calculate $\vecthreeBF{E}_{||}$($\vecthreeBF{r}$)
        \item Calculate $\vecthreeBF{a}_{E ||}$ using \fromeq{para_and_perp_acc_of_lorentz_force}
        \item Calculate $\vecthreeBF{r}$($t+dt$) using \fromeq{leapfrog_sync_x}
        \item Calculate $\vecthreeBF{v}$($t+dt$) using \fromeq{leapfrog_sync_v}
        \item Calculate new $E_t$
    \end{enumerate}
\end{itemize}
The implemenation of this logic can be observed in \fromfig{POC_core_logic}. 
\begin{figure}[H]
    \begin{minted}[linenos=true, autogobble, frame=lines, framesep=2mm, fontsize=\footnotesize]{c++}
        for (double t=0; t<SimuTime; t+=dT){
            double RelBeta  = v/c;
            double RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);

@@

            RelBeta  = v/c;
            RelGamma = 1.0 / sqrt(1.0-RelBeta*RelBeta);
            Et=RelGamma*E0; 
        }
    \end{minted}
    \caption{Core logic loop of the POC}
    \label{fig:POC_core_logic}
\end{figure}
After simulating the \textit{synchronous electron} mentioned in \fromsec{cavity_of_a_rhodotron} with $\phi_{lag}=15^\circ$ for one pass, the results from \textit{POC}, \textit{CST} and \fromeq{W_gain_each_pass_pottier} are compared.
% 40 kW total power
% Emax = 0.96 in old, 2.08 in new version
% R1 = 0.1882
% R2 = 0.753
% f = 107.5
\begin{figure}[H]
    \begin{eqnarray}
        E_{Pottier} &=& 0.565 MeV \nonumber\\
        E_{CST} &=& 0.872 MeV  \label{eq:poc_E_results}\\
        E_{POC} &=& 0.873 MeV \nonumber
    \end{eqnarray}
    \caption*{$P=40$kW, $R_1=0.188$m, $R_2=0.753$m, $f=107.5$MHz}
\end{figure}
As can be observed in \fromeq{poc_E_results}, \textit{POC software} and \textit{CST} produced very similar results. However, we cannot make the same claim regarding \fromeq{W_gain_each_pass_pottier}.
This inconsistency between $E_{Pottier}$ and $E_{CST}$ was noticed in the earlier simulations as well, which supported the idea of using another simulation software to reduce reliance on \textit{CST}.
Since using a single software would have made the process error prone.

### 2023-08-07 subsections/theory/numericalmethods/leap-frog-runge-kutta.tex
theory mostly done
multhtreading added GUI started
başlık eklendi

\subsection{Leapfrog} \label{sec:leapfrog}
The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:

\begin{equation}
    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
\end{equation}
\newline
The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space. The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion. 
It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
The idea is straight forward; in the time interval $\Delta t$, 
\begin{eqnarray}
    a(t_0) &=& f(x_0) \nonumber \\
    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
\end{eqnarray}

For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
\begin{eqnarray} \label{eq:leapfrog}
    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
\end{eqnarray}

This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.

\subsection{Runge Kutta}

The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
used to solve ordinary differential equations (ODEs) that are in the following form

\begin{equation} \label{eq:first-order-ODE}
    \parDeriv{y}{x} = f(x, y)
\end{equation}

The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
of function evaluations at different points within each step.

\begin{equation} \label{eq:general-rk}
    \begin{aligned}
        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
    \end{aligned}
    \qquad
    \begin{aligned}
        x_{n+1} = x_n + \delta x 
    \end{aligned}
\end{equation}

where

\begin{eqnarray} \label{eq:general-rk-coef}
    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
\end{eqnarray}

These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.

\begin{figure}[h!]
    \[ 
    \begin{array} 
        {c|cccc}
        0\\
        c_1 & a_{21} \\
        c_2 & a_{31} & a_{32}\\
        \vdots& & \cdots& \\
        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
        \hline
        & b_1 & b_2 &\cdots & b_m
    \end{array}
    \]
    \caption{Butcher Tableau}
    \label{fig:Butcher}
\end{figure}

The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.

\[ 
    \begin{array} 
        {c|cccc}
        0\\
        \hline
        & 1
    \end{array}
\]

The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.

\begin{figure}[h!]
    \centering
    \begin{subfigure}{.5\textwidth}
        \[ 
        \begin{array} 
            {c|cccc}
            0\\
            1/2 & 1/2 \\
            1/2 & 0 & 1/2 \\
            1   & 0 & 0 & 1\\
            \hline
            & 1/6 & 1/3 & 1/3 & 1/6
        \end{array}
        \]  
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \[ 
        \begin{array} 
            {c|cccc}
            0\\
            1/3 & 1/3 \\
            2/3 & -1/3 & 1 \\
            1   & 1 & -1 & 1\\
            \hline
            & 1/8 & 3/8 & 3/8 & 1/8
        \end{array}
        \]  
    \end{subfigure}
    \caption{Butcher Tableau for RK4}
    \label{fig:Butcher-RK4}
\end{figure}

The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}. Its main advantage is that its error coefficients are smaller than the other. But it costs more floating point operations per step. 
Resulting in slower calculations.

>>>>

\subsection{Leapfrog} \label{sec:leapfrog}
The Leapfrog method is a numerical method commonly used to solve ordinary differential equations (ODEs) that involve second-order time derivatives. Such an ODE is shown below:
\begin{equation}
    \ddot{x} = \derivS{x}{t} = f(x) \label{eq:second-order-ODE}
\end{equation}
\newline
The Leapfrog method is a variant of the finite difference method, and it approximates the solution of an ODE by discretizing both time and space. The method gets its name from the way it calculates the values of the solution at each time step, which resembles a "leapfrogging" motion. 
It is a simple and efficient algorithm that is often used in simulations of physical systems, such as celestial mechanics or molecular dynamics.
The idea is straight forward; in the time interval $\Delta t$, 
\begin{eqnarray}
    a(t_0) &=& f(x_0) \nonumber \\
    x(t_0 + \Delta t) &=& x(t_0) + v(t_0)\Delta t + a(t_0)\frac{\Delta t^2}{2} \label{eq:leapfrog_sync_x}\\
    v(t_0 + \Delta t) &=& v(t_0) + \{ a(t_0) + a(t_0 + \Delta t)\}\frac{\Delta t}{2}  \label{eq:leapfrog_sync_v}
\end{eqnarray}
For more stability, this version can be rearranged to what is called 'kick-drift-kick' form,
\begin{eqnarray} \label{eq:leapfrog}
    v(t_0 + \Delta t/2) &=& v(t_0) +  a(t_0)\frac{\Delta t}{2} \nonumber \\
    x(t_0 + \Delta t) &=& x(t_0) + v(t_0 + \Delta t/2)\Delta t \\
    v(t_0 + \Delta t) &=& v(t_0 + \Delta t/2) + a(t_0 + \Delta t)\frac{\Delta t}{2}  \nonumber
\end{eqnarray}
This version provides more time resolution to our calculation; however, it increases the number of calculations needed by about $50\%$.

\subsection{Runge Kutta} \label{sec:rungekutta}

The Runge-Kutta methods, named after the German mathematicians Carl Runge and Martin Wilhelm Kutta, family of numerical methods
used to solve ordinary differential equations (ODEs) that are in the following form
\begin{equation} \label{eq:first-order-ODE}
    \parDeriv{y}{x} = f(x, y)
\end{equation}
The basic idea behind the Runge-Kutta method is to approximate the solution of an ODE by taking small steps and using a weighted average 
of function evaluations at different points within each step.
\begin{equation} \label{eq:general-rk}
    \begin{aligned}
        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
    \end{aligned}
    \qquad
    \begin{aligned}
        x_{n+1} = x_n + \delta x 
    \end{aligned}
\end{equation}
where 
\begin{eqnarray} \label{eq:general-rk-coef}
    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
\end{eqnarray}
These \fromeqs{general-rk}{general-rk-coef} define the family of methods. To specify a perticular method, order $m$, coefficients $a_{ij}$, $b_i$ and $c_i$ should be provided.
The coefficients of any Runge-Kutta method can be visualized by a tableau called $\textit{Butcher Tableau}$.
\begin{figure}[h!]
    \[ 
    \begin{array} 
        {c|cccc}
        0\\
        c_1 & a_{21} \\
        c_2 & a_{31} & a_{32}\\
        \vdots& & \cdots& \\
        c_m & a_{m1} & a_{m2} & \cdots & a_{m,m-1}\\
        \hline
        & b_1 & b_2 &\cdots & b_m
    \end{array}
    \]
    \caption{Butcher Tableau}
    \label{fig:Butcher}
\end{figure}
The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
\[ 
    \begin{array} 
        {c|cccc}
        0\\
        \hline
        & 1
    \end{array}
\]
The most commonly used version of the Runge-Kutta method is the fourth-order Runge-Kutta method, also known as RK4. 
The RK4 method involves four function evaluations per step and has an error term that is proportional to the step size raised to the fifth power.
Two of the most used \textit{Butcher tableaus} for \textit{RK4} given below.
\begin{figure}[h!]
    \centering
    \begin{subfigure}{.5\textwidth}
        \[ 
        \begin{array} 
            {c|cccc}
            0\\
            1/2 & 1/2 \\
            1/2 & 0 & 1/2 \\
            1   & 0 & 0 & 1\\
            \hline
            & 1/6 & 1/3 & 1/3 & 1/6
        \end{array}
        \]  
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \[ 
        \begin{array} 
            {c|cccc}
            0\\
            1/3 & 1/3 \\
            2/3 & -1/3 & 1 \\
            1   & 1 & -1 & 1\\
            \hline
            & 1/8 & 3/8 & 3/8 & 1/8
        \end{array}
        \]  
    \end{subfigure}
    \caption{Butcher Tableau for RK4}
    \label{fig:Butcher-RK4}
\end{figure}
The second tableau in \fromfig{Butcher-RK4} is called the \textit{"3/8 rule"}. Its main advantage is that its error coefficients are smaller than the other. But it costs more floating point operations per step. 
Resulting in slower calculations.

### 2023-08-07 subsections/theory/rhodotron/rhodotron.tex
başlık eklendi

Particle accelerators are essential tools for scientific research. They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics. 
Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.

% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{A linear proton accelerator in KAHVELab}
\end{figure}

\subsection{Key Concepts}

@@

According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.

% TODO : ADD STEERER MAGNET PICTURE HERE
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{A bending magnet used in KAHVELab}
\end{figure}

@@

In the table below, optimized characteristics of a rhodotron cavity can be observed. 
\begin{figure}[H]
    \centering
    \includegraphics[width=.9\textwidth]{../../../figures/pottier_table1.png}
    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
    \label{fig:pottier_table1}
\end{figure}

Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.

Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
\begin{equation}
    \label{eq:W_gain_each_pass_pottier}
    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
\end{equation}

Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.

Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
\begin{figure}[H]
    \centering
    \includegraphics[width=.9\textwidth]{../../../figures/pottier_table2.png}
    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
    \label{fig:pottier_table2}
\end{figure}

Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
\begin{equation}
    \label{eq:W_total_gain_pottier}
    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
\end{equation}

@@

This process is explained further in the following figures where $T$ is the period of the electric field.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod1.pdf}
    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod2.pdf}
    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_2}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod3.pdf}
    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_3}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod4.pdf}
    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_4}
\end{figure}

>>>>

Particle accelerators are essential tools for scientific research. They enable scientists to probe the fundamental constituents of matter, study particle interactions, and explore the laws of physics. 
Accelerators have been instrumental in discovering and characterizing fundamental particles, such as quarks, leptons, and the Higgs boson. 
They also facilitate the production of high-intensity beams for applications in material science, radiotherapy, and industrial processes like particle irradiation and sterilization.
% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{A linear proton accelerator in KAHVELab}
\end{figure}
\subsection{Key Concepts}

@@

According to the Lorentz Force Law ( $\textit{Section \ref{sec:lorentz-force}}$ ), when a charged particle moves through a magnetic field, it experiences a force perpendicular to both its velocity 
vector and the magnetic field direction. This force causes the particle's trajectory to curve, resulting in a bending effect.
% TODO : ADD STEERER MAGNET PICTURE HERE
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{A bending magnet used in KAHVELab}
\end{figure}

@@

In the table below, optimized characteristics of a rhodotron cavity can be observed. 
\begin{figure}[H]
    \centering
    \includegraphics[width=.9\textwidth]{../../../figures/pottier_table1.png}
    \caption{Optimized characteristics of a rhodotron cavity \cite{rhodo_pottier}}
    \label{fig:pottier_table1}
\end{figure}
Here, $p$ is the integer multiplier in the equation ($l=p\lambda$) mentioned above, $R_1$ is the radius of the inner cylinder, $R_2$ is the radius of the outer cylinder, 
$Z_{se}$ is effective shunt empedance, $Z_{sp}$ is practical shunt empedance which was taken to be $0.85 Z_{se}$.

Energy gain after each pass can be calculated by the following formula \cite{rhodo_pottier}
\begin{equation}
    \label{eq:W_gain_each_pass_pottier}
    W_1 = Z_{sp}^{1/2} P^{1/2} cos \phi  
\end{equation}
Where $P$ is the dissipated power, $\phi$ is the phase lag, taken as $15^\circ$ \cite{rhodo_pottier}.

Considering $Z_{sp} \propto \lambda^{1/2}$, \,\,\, $W_1 \propto \lambda^{1/4}$, \,\,\,   $V \propto \lambda^3$, where $V$ is the volume of the cavity, implementing the $p=1$ design in \fromfig{pottier_table1} is much more space efficient.
\begin{figure}[H]
    \centering
    \includegraphics[width=.9\textwidth]{../../../figures/pottier_table2.png}
    \caption{Energy of a synchronous electron after each pass for both $p=1$ and $p=2$ \cite{rhodo_pottier}}
    \label{fig:pottier_table2}
\end{figure}
Total energy gain after n passes $W$ can then be found by \fromeq{W_gain_each_pass_pottier}, taking $\phi = 15^\circ$, $p=1$, i.e $R_2 = 0.27 \lambda$.
\begin{equation}
    \label{eq:W_total_gain_pottier}
    W \approx 2.14 \lambda^{1/4} P^{1/2} n \quad keV
\end{equation}

@@

This process is explained further in the following figures where $T$ is the period of the electric field.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod1.pdf}
    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_1}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod2.pdf}
    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_2}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod3.pdf}
    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_3}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod4.pdf}
    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_4}
\end{figure}
